Measuring Individual Partisan Harm in Redistricting

### 2021-09-11 paper/paper.Rmd
pairs

Figure \ref{fig:nj-maps} shows the baseline Democratic vote share by precinct, along with two hypothetical gerrymanders of the state, which were generated using the short-burst optimization approach of @cannon2020.

@@

\clearpage

\appendix

# Proofs of Propositions {#app:proofs}

@@

>>>>

Figure \ref{fig:nj-maps} shows the baseline Democratic vote share by precinct, along with two hypothetical gerrymanders of the state, which were generated using the short-burst optimization approach of @cannon2020.
The Democratic gerrymander has 11 Democratic seats and 1 Republican seat at baseline, while the Republican gerrymander has 6 Democratic and 6 Republican seats.

@@

```{=tex}
\clearpage
\appendix
\renewcommand\thefigure{\thesection.\arabic{figure}}
\setcounter{figure}{0}
```
# Proofs of Propositions {#app:proofs}

@@

# Relationship Between Districting Metrics in New Jersey {#app:nj}

```{r nj-pairs, fig.cap="Scatterplots for all pairs of metrics. Color indicates the number of Democratic seats won (ranging from 7 to 10). Below the diagonal, numbers indicate the absolute value of the correlation between variables.", fig.width=7, fig.height=7}
include_graphics(here("paper/figures/nj_pairs.pdf"))
```
